Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package

### 2017-11-24 docs/manuscript.tex
Updating the MS

\section{Interobserver Variability and Validation}
%% simulated data
%% x people doing y plots
\subsection{Methods}
We evaluated the consistency of digitisation using \pkg{metaDigitise} and tested how well digitisations estimate the true underlying data. This was accomplished by simulating a dataset with two different groups and two traits, and these data were then used to construct four different plot types (scatterplot, mean and error, histogram and boxplots). Each variable was plotted twice for a given plot type (figures were modified slightly to give users a sense that they were digitising new data) generating a total of 14 figures. We randomised the order of these figures (using the same data) and provdied the entire figure directory to a total of 15 indpendent digitisers. The same data was presented twice for each figure type to estimate between- and within- user variability (i.e., the intra-class correlation coefficient) in the data. Digitisers varied in their level of experience from those having done meta-analyses or comparative work to those not having any experience doing so. We got users to digitise all 14 figures and then send the data on these to evaluate interobserver variablity.

We analysed these data using linear mixed effect models with user identify as a random effect. The overall model also included plot type to account for the different means across the variables and plots. We used the mean, standard deviation and correlation coeficients as response variables in three seperate models. If digitisations were consistent across all users then we would predict no significant between user variability in the data. We also qualitatively report how close the average digitised mean, SD and correlation coefficient were to the actual mean values of traits presented in the figures.

@@

>>>>

\section{Interobserver Variability and Validation}
%% simulated data
%% x people doing y plots
\subsection{Interobserver variability in digitisations}
We evaluated the consistency of digitisation using \pkg{metaDigitise} by simulating a dataset with two different groups and two traits. These data were then used to construct four different plot types (scatterplot, mean and error, histogram and boxplots). Each variable was plotted twice for a given plot type (figures were modified slightly to give users a sense that they were digitising new data) generating a total of 14 figures. We randomised the order of these figures (using the same data) and provided the entire figure directory to a total of 15 indpendent digitisers. The same data was presented at least twice for each figure type to estimate between- and within- user variability (i.e., the intra-class correlation coefficient) in the data. Digitisers varied in their level of experience from those having done meta-analyses or comparative work to those not having any experience doing so. We got users to digitise all 14 figures and then send the data on these to evaluate interobserver variablity across the plots.

We analysed these data by first transformting each users mean, standard deviation and correlation coefficient generated from their digitisations to standardized mean differences (in otherwords, deviations were percentage differences from the true summary statistics). We then estimated intra-class correlation coefficients (ICC) (adjusted - accounting for covariates and unadjusted - not accounting for covariates) using linear mixed effect models with user identify as a random effect. We tested the significance of ICC estimates using liklihood ratio tests based on 1000 parametric bootstraps of the model. The overall model also included plot type, variable and group to account for possible biases across the variables and plots. We used standardised mean, standard deviation and correlation coeficients as response variables in seperate models using both \pkg{lme4} \citep{bates2015} and \pkg{MCMCglmm} \citep{hadfield2010}, estimating ICC using the \pkg{rptR} package \citep{stoffel2017} in R. If digitisations were consistent across all users then we would predict no significant between user variability in the data.

@@

  Across plot types we found no evidence for any inter-observer variability in digitisations for the mean (Unadjusted ICC = 0, 95 CI = 0 to 0.029, p = 1; Adjusted ICC = 0, 95 CI = 0 to 0.033, p = 1), standard deviation (Unadjusted ICC = ; Adjusted ICC = ) or correlation coefficient (Unadjusted ICC = ; Adjusted ICC = )
